Lucy.js: Client-Side Indexes for Fast Full-Text Searching

### 2014-12-11 paper/paper.tex
Weird merge conflicts
Added inverted index figure

\title{Client-Side Indexes for Fast Full-Text Searching}

@@

\begin{figure}[]
   \includegraphics[scale=.43]{arch}
  \caption{caption here.}
\end{figure}

@@

>>>>

\title{Lucy.js: Client-Side Indexes for Fast Full-Text Searching}

@@

\begin{figure}[]
	\includegraphics[scale=.43]{arch}
	\caption{Architecture of Lucy.js}
\end{figure}

@@

\begin{figure}
  \centering
   \includegraphics[scale=.35]{inverted-index}
  \caption{Structure of a simplified inverted index, as it would be stored in IndexedDB. Note that our implementation also includes additional information about the position of the tokens in the document (among other things), for better ranking}
\end{figure}
